P4Query: Static Analyser Framework for P4

### 2021-03-27 publications/The_tool_intro/paper.tex
tool_intro: minor changes

By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to to implement different end-users services, by reusing the same static code analysis operations.
See Section~\ref{sec:apps} for a few examples of applications built on top of the P4Query.
In systems with uniform APIs, programmers have to learn only one paradigm to maintain, extend or otherwise alter the system (e.g. in case of P4C, visitors and passes are the main concepts of such a uniform API).

@@

Our second design goal, \textit{ease of extensibility} is illustrated by Figure~\ref{fig:arch-deps}, that elaborates the application and infrastructure layers. 
This arrangement was inspired by declarative build systems and the blackboard pattern used in distributed MI.

>>>>

By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to implement different end-users services, by reusing the same static code analysis operations.
See Section~\ref{sec:apps} for a few examples of applications built on top of the P4Query.
In systems with uniform APIs, programmers have to learn only one paradigm to maintain, extend or otherwise alter the system (e.g. in case of P4C, visitors and passes are the main concepts of such a uniform API).

@@

Our second design goal, \textit{ease of extensibility} is illustrated by Figure~\ref{fig:arch-deps}, that elaborates the application and infrastructure layers. 
This arrangement was inspired by declarative build systems and the blackboard pattern used in distributed AI.
